\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=0.6in, top=0.5in, bottom=0.5in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{newtxtext,newtxmath}

\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue!60!black}

\titleformat{\section}{\large\bfseries\vspace{2pt}}{}{0em}{}[\vspace{-4pt}\rule{\linewidth}{0.4pt}]
\titlespacing{\section}{0pt}{8pt}{4pt}

\setlist[itemize]{leftmargin=*, itemsep=1pt, parsep=0pt, topsep=2pt}
\setlist[enumerate]{leftmargin=*, itemsep=3pt, parsep=0pt, topsep=2pt}

\setlength{\parskip}{0pt}

\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE \textbf{Jaemin Kim}} \\[4pt]
  Department of Physics, Yonsei University, Seoul, South Korea \\[2pt]
  \href{mailto:abcdvd131@gmail.com}{abcdvd131@gmail.com}
  \quad$\cdot$\quad
  \href{https://github.com/abcdvd}{GitHub}
  \quad$\cdot$\quad
  \href{https://abcdvd.github.io}{Homepage}
\end{center}

\section*{Education}
\textbf{Yonsei University}, Seoul, South Korea \hfill Mar. 2021 -- Present \\
B.S. in Physics, College of Science
\begin{itemize}
  \item GPA: 3.69\,/\,4.3 \quad|\quad Academic Excellence Scholarship (50\% tuition waiver), Spring 2024
  \item Military service: May 2022 -- Nov. 2023
\end{itemize}

\section*{Research Experience}
Computational Intelligence \& Photography Lab, Yonsei University \hfill Jun. 2025 -- Present \\
Research Intern, advised by Prof.\ Seon Joo Kim

\section*{Publications}
\begin{enumerate}[label={[\arabic*]}]
  \item Jihye Yoo, \textbf{Jaemin Kim}, Jinwoo Kim, Seon Joo Kim.
    ``\href{https://openreview.net/forum?id=zKyrO2WDA0}{Tone-Aware Diffusion: Enabling Tone-on-Tone and Tone-in-Tone Generation}.''
    HiGen Workshop @ CVPR 2026. \textbf{Best Paper Runner-up.}
  \item \textbf{Jaemin Kim}, Jinwoo Kim, Seon Joo Kim.
    ``Freeze the Structure, Free the Color: Fourier-Domain Training for Unpaired Smartphone ISP.''
    NTIRE Workshop @ CVPR 2026. \textbf{3rd Place, NTIRE 2026 Challenge.}
\end{enumerate}

\section*{Research Interests}
Computational Photography, Image Restoration, Diffusion Models, Reinforcement Learning, Physical Simulation

\section*{Projects}
\textbf{\href{https://www.youtube.com/watch?v=gmeZ6BD5u0w}{Autonomous Indoor Flight of Tello Drone using CrossFormer}} \hfill Yonsei Drone Club
\begin{itemize}
  \item Designed a vision-based indoor autonomous navigation system using the CrossFormer model.
  \item Contributed to data collection, inference code development, and test flights.
\end{itemize}

\smallskip

\textbf{\href{https://github.com/abcdvd/snake-game-reinforcement-learning}{Reinforcement Learning for Snake Game}} \hfill Personal Project
\begin{itemize}
  \item Built a reinforcement learning agent using PyTorch to learn the classic Snake game.
\end{itemize}

\smallskip

\textbf{\href{https://github.com/abcdvd/league-of-legends-winner-predicting}{Real-Time Win Prediction for League of Legends}} \hfill Personal Project
\begin{itemize}
  \item Collected match data using Riot Games API and built a win-rate prediction model.
\end{itemize}

\section*{Technical Skills}
\begin{itemize}
  \item \textbf{Languages:} Python (PyTorch, TensorFlow, JAX) \quad|\quad \textbf{Tools:} Git, Linux
\end{itemize}

\section*{Awards \& Activities}
\begin{itemize}
  \item 15th Place, Yonsei University Algorithm Programming Contest, 2023
\end{itemize}

\end{document}
